rotation_runs2019

### 2019-11-20 inst/documents/rotation_runs2019.Rmd
delete old data and figs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

>>>>

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'
